Denotational Semantics of General Payment Primitives, and Its Payment System

### 2022-09-27 packages/spec-haskell/yellowpaper/Paper.tex
subsection Money Mediums!!

Here we present a formal definition of payment system and its components.

@@

\subsection{Money Medium Models}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

An attempt of creating a unifying theory for money and its distribution was made by Buldas, Saarepera et
al.\cite{buldas2021unifying}

\begin{displayquote}
A useful observation about existing money schemes is that they all have some kind of monetary units that are physical or
digital representations of money. Examples are bills, coins, bank accounts, Bitcoin UTXOs,
etc. \cite{buldas2021unifying}
\end{displayquote}

@@

>>>>

Here we present a definition of payment system and its components.

@@

\subsection{Money Mediums}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{displayquote}
A useful observation about existing money schemes is that they all have some kind of monetary units that are physical or
digital representations of money. Examples are bills, coins, bank accounts, Bitcoin UTXOs,
etc. \footfullcite[][P3]{buldas2021unifying}
\end{displayquote}

We call these money mediums. And we further separate them into two big groups:

\begin{itemize}
\item \textit{Token and Its Accounts} - E.g. bank currency accounts. Each token is its own centralized execution
    environment, bearers access their monetary value through their accounts, and execute financial contracts through the
    token.
\item \textit{Note} - E.g. federal reserve notes, bills, coins and Bitcoin UTXOs, etc. The execution environment is
    independent of the notes, but it needs notes to complete the execution of financial contracts.
\end{itemize}

One of the main differences is from the ``user interface'' perspective. A bearer expects to keep many notes at hand,
while maybe only needs a few accounts for each token. Also it is up to bearers to keep track of all their notes, while
token can keep track of most of the states for bearers; hence notes are more decentralized and tokens are more
centralized. Some also argue note-like model is better for complex concurrent and distributed computing environment
\footfullcite[][P2]{chakravarty2020extended}.

\subsubsection{Haskell Definition Of Money Mediums}

\input{MoneyMedium.lhs.tex}

@@

\section{Complexity Argument}
